|

### 2021-12-10 front-and-back-matter/99-appendices.Rmd
Range of changes to the appendixx

<!-- __To be copied from email__ -->

@@

<!----------------------------------------------------------------------------->
(ref:missingMatrix-caption) Overview of missing data across covariates included in IPD analysis. Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.

@@

@@

Unfortunately, given the nature of the data underpinning the CPRD (Chapter \@ref(cprd-analysis-heading)) and IPD (Chapter \@ref(ipd-heading)) analyses, it is not possible to make it publicly available. Access to the CPRD data is dependent on an application to its managing body, while acces to the cohorts within the DPUK requires approval from both the DPUK and inidividual cohort owners. IN the absence of data sharing, the best option to enable review and increase transparency is the open sharing of the code used to perform the analysis.

@@

>>>>

<!-- TODO __To be copied from email__ -->

@@

<!----------------------------------------------------------------------------->
(ref:missingMatrix-caption) Overview of missing data across covariates (described as N (%)) included in IPD analysis. Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.

@@

### Comparison with previous analysis of the Whitehall II cohort {#appendix-ipd-whitehall}

<!----------------------------------------------------------------------------->
(ref:whitehallComparisonAd-cap) Comparison of results across the two analysis of the Whitehall II cohort for the Alzheimer's disease outcome.

(ref:whitehallComparisonAd-scap) Comparison of results across the two analysis of the Whitehall II cohort

```{r whitehallComparisonAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonAd-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonAd-scap)'}
knitr::include_graphics(file.path("figures/ipd/whitehall_comparison_ad.png"))
```
<!----------------------------------------------------------------------------->

@@

Unfortunately, given the nature of the data underpinning the CPRD (Chapter \@ref(cprd-analysis-heading)) and IPD (Chapter \@ref(ipd-heading)) analyses, it is not possible to make it publicly available. Access to the CPRD data is dependent on an application to its managing body, while acces to the cohorts within the DPUK requires approval from both the DPUK and inidividual cohort owners. In the absence of data sharing, the best option to enable review and increase transparency is the open sharing of the code used to perform the analysis.[@goldacre2019]

@@

OVer the course of my PhD, I kept a record of attempted
